Backpropagating Gravitational wave events

### 2022-04-13 src/ms.tex

@@

>>>>

\section{Method Rewrite}
\label{sec:method-rewrite}

\wf{Re-writing the methods section with a new viewpoint, gonna try to eventually merge the content.}

Once all the parameters including a particular draw of all the random variables
represented by $\bm{X}$ are known, the population synthesis code is a
deterministic function that transforms the properties of the progenitors into
the GW parameters $\bm{\theta}$:
\begin{equation}
    \bm{\theta} = \bm{f}\left( \bm{\Theta} \right).
\end{equation}
The mapping $\bm{f}$ from $\bm{\Theta}$ to $\bm{\theta}$ is many-to-one.  
In order to draw inferences about $\bm{\Theta}$ from gravitational wave data, we
need to be able to evaluate the likelihood of that data at fixed progenitor
parameters, 
\begin{equation}
    p\left( d \mid \bm{\Theta} \right) = p\left( d \mid \bm{\theta} = \bm{f}\left( \bm{\Theta} \right) \right),
\end{equation}
because the likelihood depends only on the gravitational waveform generated by
parameters $\bm{\theta}$ to which the progenitor parameters map.  In principle
this likelihood could be computed at arbitrary vaues of $\bm{\Theta}$ using the
same machinery that is used to estimate source parameters in gravitational wave
catalogs \citep{Veitch2015,Ashton2019,Romero-Shaw2020,GWTC-3} to develop samples
of progenitor parameters, hyper-parameters, and random variables in
$\bm{\Theta}$ from a posterior density.

However, it is very expensive to couple progenitor evolution to stochastic
sampling in this way.  Because the gravitational wave likelihood function
ultimately depends only on the GW parameters $\theta$, and catalogs have already
produced samples over these parameters from a posterior density 
\begin{equation}
    p\left( \bm{\theta} \mid d \right) \propto p\left( d \mid \bm{\theta} \right) p_\mathrm{GW} \left( \bm{\theta} \right),
\end{equation}
where $p_\mathrm{GW}$ is the prior density used for sampling, it is much more
efficient to \wf{WIP}.

@@

\bibliography{bib}
